How wise is the crowd: Can we infer people are accurate and competent merely because they agree with each other?

### 2024-09-11 appendix_exp6.Rmd
update paper revisions round 1

```{r stimuli-10, echo=FALSE}
# Create a matrix of image file paths as Markdown-formatted strings
image_paths <- data.frame(
  condition = c("opposing majority (0)", "dissensus (1)", "majority (2)", "consensus (10)"),
  imgage_a = c(
    "![](Experiment_6/figures/stimuli/minority_10_a.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/divergence_10_a.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/majority_10_a.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/consensus_10_a.png){ width=40% }"
  ),
  imgage_b = c(
    "![](Experiment_6/figures/stimuli/minority_10_b.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/divergence_10_b.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/majority_10_b.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/consensus_10_b.png){ width=40% }"
  )
)

@@

```{r stimuli-10-alt, echo=FALSE}
# Create a matrix of image file paths as Markdown-formatted strings
image_paths <- data.frame(
  condition = c("opposing majority (0)", "dissensus (1)", "majority (2)", "consensus (10)"),
  imgage_a = c(
    "![](Experiment_6/figures/stimuli/minority_10_a_alt.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/divergence_10_a_alt.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/majority_10_a_alt.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/consensus_10_a_alt.png){ width=40% }"
  ),
  imgage_b = c(
    "![](Experiment_6/figures/stimuli/minority_10_b_alt.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/divergence_10_b_alt.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/majority_10_b_alt.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/consensus_10_b_alt.png){ width=40% }"
  )
)

>>>>

```{r stimuli-10, echo=FALSE}
# Create a matrix of image file paths as Markdown-formatted strings
image_paths <- data.frame(
  condition = c("minority (0)", "dissensus (1)", "majority (2)", "consensus (3)"),
  imgage_a = c(
    "![](Experiment_6/figures/stimuli/minority_10_a.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/divergence_10_a.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/majority_10_a.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/consensus_10_a.png){ width=40% }"
  ),
  imgage_b = c(
    "![](Experiment_6/figures/stimuli/minority_10_b.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/divergence_10_b.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/majority_10_b.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/consensus_10_b.png){ width=40% }"
  )
)

@@

```{r stimuli-10-alt, echo=FALSE}
# Create a matrix of image file paths as Markdown-formatted strings
image_paths <- data.frame(
  condition = c("minority (0)", "dissensus (1)", "majority (2)", "consensus (3)"),
  imgage_a = c(
    "![](Experiment_6/figures/stimuli/minority_10_a_alt.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/divergence_10_a_alt.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/majority_10_a_alt.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/consensus_10_a_alt.png){ width=40% }"
  ),
  imgage_b = c(
    "![](Experiment_6/figures/stimuli/minority_10_b_alt.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/divergence_10_b_alt.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/majority_10_b_alt.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/consensus_10_b_alt.png){ width=40% }"
  )
)
